Multi-channel Kondo model URG

### 2021-11-25 notes/multi-channel-urg.tex
started calculating  real space effective Hamiltonian

\section{Derivation of low energy effective \(k-\)space Hamiltonian }

@@

To calculate these effective Hamiltonians, we will calculate the individual terms. We can easily simplify the \(S_d^z\) in the denominator of \(G_0\), because \(S_d^\pm \frac{1}{A + B S_d^z} = S_d^\pm \frac{1}{A \mp \frac{1}{2}B}\):
\begin{equation}\begin{aligned}
	V G_0 V^\dagger = \frac{J^2}{4} s_\text{tot}^- \frac{\frac{1}{2} + S_d^z}{E_\text{gs} + \frac{J}{2} s_\text{tot}^z - H_0} s_\text{tot}^+ \\
	V^\dagger G_0 V = \frac{J^2}{4} s_\text{tot}^+ \frac{\frac{1}{2} - S_d^z}{E_\text{gs} - \frac{J}{2} s_\text{tot}^z - H_0} s_\text{tot}^-
\end{aligned}\end{equation}
Since \(H_0\) does not commute with the spin operators, we will need to expand the denominator to make sense of this Hamiltonian.
\begin{equation}\begin{aligned}
	 V G_0 V^\dagger =  s_\text{tot}^- \frac{1}{E_\text{gs} + \frac{J}{2} s_\text{tot}^z}\left[1 + \frac{1}{E_\text{gs} + \frac{J}{2} s_\text{tot}^z}H_0 + \frac{1}{E_\text{gs} + \frac{J}{2} s_\text{tot}^z}H_0\frac{1}{E_\text{gs} + \frac{J}{2} s_\text{tot}^z}H_0 + \ldots\right] s_\text{tot}^+\\
	 V^\dagger G_0 V =  s_\text{tot}^+ \frac{1}{E_\text{gs} - \frac{J}{2} s_\text{tot}^z}\left[1 + \frac{1}{E_\text{gs} - \frac{J}{2} s_\text{tot}^z}H_0 + \frac{1}{E_\text{gs} - \frac{J}{2} s_\text{tot}^z}H_0\frac{1}{E_\text{gs} - \frac{J}{2} s_\text{tot}^z}H_0 + \ldots\right] s_\text{tot}^-
\end{aligned}\end{equation}
This is an expansion in \(H_0^n/J^{n+1}, n=0,1,2,\ldots\). The \(n=0\) terms give
\begin{equation}\begin{aligned}
	s_\text{tot}^- \frac{1}{E_\text{gs} + \frac{J}{2} s_\text{tot}^z}s_\text{tot}^+ = s_\text{tot}^- s_\text{tot}^+ \frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z + 1\right)} %= \left[s_\text{tot}\left( s_\text{tot}+1 \right)  - s_\text{tot}^z\left( s_\text{tot}^z + 1 \right) \right] \frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z + 1\right)}\\ 
	\\
	s_\text{tot}^+ \frac{1}{E_\text{gs} - \frac{J}{2} s_\text{tot}^z}s_\text{tot}^- = s_\text{tot}^+ s_\text{tot}^- \frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)}% = \left[s_\text{tot}\left( s_\text{tot}+1 \right)  - s_\text{tot}^z\left( s_\text{tot}^z - 1 \right) \right] \frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)}
\end{aligned}\end{equation}

@@

>>>>

\section{Effective Hamiltonian for low-energy excitations: \(k-\)space}

@@

To calculate these effective Hamiltonians, we will calculate the individual terms. We can easily simplify the \(S_d^z\) in the denominator of \(G_0\), because \(S_d^\pm \frac{1}{A + B S_d^z} = S_d^\pm \frac{1}{A \mp \frac{1}{2}B}\):
\begin{equation}\begin{aligned}
	V G_0 V^\dagger = \frac{J^2}{4} s_\text{tot}^- \frac{\frac{1}{2} + S_d^z}{E_\text{gs} + \frac{J}{2} s_\text{tot}^z - H_0} s_\text{tot}^+ \\
	V^\dagger G_0 V = \frac{J^2}{4} s_\text{tot}^+ \frac{\frac{1}{2} - S_d^z}{E_\text{gs} - \frac{J}{2} s_\text{tot}^z - H_0} s_\text{tot}^-
\end{aligned}\end{equation}
Since \(H_0\) does not commute with the spin operators, we will need to expand the denominator to make sense of this Hamiltonian.
\begin{equation}\begin{aligned}
	 V G_0 V^\dagger =  s_\text{tot}^- \frac{1}{E_\text{gs} + \frac{J}{2} s_\text{tot}^z}\left[1 + \frac{1}{E_\text{gs} + \frac{J}{2} s_\text{tot}^z}H_0 + \frac{1}{E_\text{gs} + \frac{J}{2} s_\text{tot}^z}H_0\frac{1}{E_\text{gs} + \frac{J}{2} s_\text{tot}^z}H_0 + \ldots\right] s_\text{tot}^+\\
	 V^\dagger G_0 V =  s_\text{tot}^+ \frac{1}{E_\text{gs} - \frac{J}{2} s_\text{tot}^z}\left[1 + \frac{1}{E_\text{gs} - \frac{J}{2} s_\text{tot}^z}H_0 + \frac{1}{E_\text{gs} - \frac{J}{2} s_\text{tot}^z}H_0\frac{1}{E_\text{gs} - \frac{J}{2} s_\text{tot}^z}H_0 + \ldots\right] s_\text{tot}^-
\end{aligned}\end{equation}
This is an expansion in \(H_0^n/J^{n+1}, n=0,1,2,\ldots\). The \(n=0\) terms give
\begin{equation}\begin{aligned}
	s_\text{tot}^- \frac{1}{E_\text{gs} + \frac{J}{2} s_\text{tot}^z}s_\text{tot}^+ = s_\text{tot}^- s_\text{tot}^+ \frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z + 1\right)} %= \left[s_\text{tot}\left( s_\text{tot}+1 \right)  - s_\text{tot}^z\left( s_\text{tot}^z + 1 \right) \right] \frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z + 1\right)}\\ 
	\\
	s_\text{tot}^+ \frac{1}{E_\text{gs} - \frac{J}{2} s_\text{tot}^z}s_\text{tot}^- = s_\text{tot}^+ s_\text{tot}^- \frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)}% = \left[s_\text{tot}\left( s_\text{tot}+1 \right)  - s_\text{tot}^z\left( s_\text{tot}^z - 1 \right) \right] \frac{1}{E_\text{gs} - \frag{J}{2} \left(s_\text{tot}^z - 1\right)}
\end{aligned}\end{equation}

@@

\section{Effective Hamiltonian for low-energy excitations: real space}
We will obtain the theory for the low-energy excitations of the two-channel Kondo model by treating the hopping between the zeroth site and the first site as a perturbation. The zeroth site is just the spin-exchange part of the Hamiltonian:
\begin{equation}\begin{aligned}
	H_0 = J \vec{S_d}\cdot\vec{s}_\text{tot}, V = -t \sum_{\sigma,l}c^\dagger_{0\sigma,l}c_{1\sigma,l} + \text{h.c.}
\end{aligned}\end{equation}
We will remove this single-particle interaction through a Schrieffer-Wolf transformation and generate higher order interactions in the process. The renormalization due to to this process, up to second order, is given by
\begin{equation}\begin{aligned}
	\Delta H = V \frac{1}{E_\text{gs} - H_0}V
\end{aligned}\end{equation}
The two degenerate ground states are
\begin{equation}\begin{aligned}
	\ket{\Psi_\sigma} = \frac{1}{\sqrt 6} \left[\ket{\sigma, \overline \sigma,\overline \sigma} - \ket{\overline \sigma,\sigma,\sigma} - \ket{\overline \sigma,\overline \sigma,\sigma}\right], && \sigma=\pm 1
\end{aligned}\end{equation}
where \(\ket{\pm 1} = \ket{\uparrow},\ket{\downarrow}\) and the notation is as follows: the first label is for the impurity spin and the second and third labels are for the zeroth sites of channels 1 and channel 2 respectively. We will calculate the effective Hamiltonian in the subspace of a single ground state:
\begin{equation}\begin{aligned}
	\Delta H_\sigma = \ket{\Psi_\sigma}\bra{\Psi_\sigma}V \frac{1}{E_\text{gs} - H_0}V\ket{\Psi_\sigma}\bra{\Psi_\sigma}
\end{aligned}\end{equation}
Since the perturbation also acts on the first site (the site nearest to the zeroth site), we will need to expand the basis:
\begin{equation}\begin{aligned}
	\ket{\Psi_\sigma} = \frac{1}{\sqrt 6} \left[\ket{\sigma, \overline \sigma,\overline \sigma} - \ket{\overline \sigma,\sigma,\sigma} - \ket{\overline \sigma,\overline \sigma,\sigma}\right]\otimes\prod_{\alpha=\pm 1, l=1,2} \sum_{n^1_{\alpha,l}=0,1}\ket{n^1_{\alpha,l}}, && \sigma=\pm 1
\end{aligned}\end{equation}
Here, \(n^1_{\alpha,l}\) denotes the number of electrons of spin \(\alpha\) and channel index \(l\) on the first site.

The action of the perturbation on the state is given by
\begin{equation}\begin{aligned}
	V\ket{\Psi_\sigma} = \left(-t \sum_{\beta,l}c^\dagger_{0\beta,l}c_{1\beta,l} + \text{h.c.}\right) \frac{1}{\sqrt 6} \left[\ket{\sigma, \overline \sigma,\overline \sigma} - \ket{\overline \sigma,\sigma,\sigma} - \ket{\overline \sigma,\overline \sigma,\sigma}\right]\otimes\prod_{\alpha=\pm 1, l=1,2} \sum_{n^1_{\alpha,l}=0,1}\ket{n^1_{\alpha,l}}
\end{aligned}\end{equation}
We will split the perturbation into parts: \(V = \sum_\sigma \left(v_\sigma + v_\sigma^\dagger\right) \), where \(v\) is the part that annihilates an electron on the first site.
